From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/manynames.tex
Redo paragraph in 3.3 about entry-names being instance-based, with more convincing stats, to emphasize that it's nice to have verified data.

\cs{Make consistent with what is (was) in the intro wrt formulation:}
Let us focus on our two main reasons for using \mn to evaluate computational models, i.e., a dataset where actual contextualized instances are named (not prototypes or classes), and where every instance is named by many annotators.
Regarding the first, we can show that different instances of the same class can differ in entry-level name.

\mw{Old stuff here, currently redoing but Carina was too impatient so I had to push:}
In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name. The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names). Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators. We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g. \name{boy-player}, \textit{sandwich-food}, \name{building-church}, ...).

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account:
by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

>>>>

Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
\cs{Make formulation consistent with what is (was) in the intro:}
Regarding feature (i), recall that the traditional, taxonomic view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name. 
Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
To quantify this point, let us concentrate on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a very strict requirement which only 281 of the 422 entry-level names of \mn meet.
These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (SD: .34).
Now, some of this is due to errors of the type we have sought to identify, but the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, but skewed with about half over 80\%).

%provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names). We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g. \name{boy-player}, \textit{sandwich-food}, \name{building-church}, ...).

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason, feature (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account:
by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
